Expected Dependency Pair Match:\\ Predicting improvements to {HTER} with expected syntactic structure

### 2009-05-08 mtjournal.tex
fleshed out title and opening

\begin{document}                                                                                   
\begin{article}
\begin{opening}         
\title{A Sample Document\thanks{Footnote 
            to the title with the `thanks' command.}} 
\author{Leslie \surname{Lamport}}  
\runningauthor{Leslie Lamport}
\runningtitle{A Sample Document}
\institute{Author's Affiliation}
\date{April 15, 1993}

\begin{abstract}
This is a sample input file.  Comparing it with the output it
generates can show you how to produce a simple document of
your own.
\end{abstract}
\keywords{sample, \LaTeX}

>>>>

\begin{document}                                                                                   
\begin{article}
\begin{opening}         
\title{Expected Dependency Pair Match:\\
Predicting improvements to {HTER} with expected syntactic structure} 
\author{Jeremy G. \surname{Kahn}\email{jgk@u.washington.edu}}  
\institute{University of Washington}
\author{Matthew \surname{Snover}\email{snover@cs.umd.edu}}
\institute{University of Maryland}
\author{Mari \surname{Ostendorf}\email{ostendor@u.washington.edu}}  
\institute{University of Washington}
\runningauthor{Kahn, Snover \& Ostendorf}
\runningtitle{Expected Dependency Pair Match}
\date{May 10, 2009}

\begin{abstract}
Abstract to go here
\end{abstract}
\keywords{machine translation evaluation, syntax, dependency trees}
